Model LF

### 2022-10-20 max_dp endogen stød.Rmd
Commit

COMMENT> 
IDENTITY> max_gap
EQ> max_gap = 0.4
IF> sens2_low <= 0 & sens2_up <= 0
IDENTITY> max_gap
EQ> max_gap = 0.42
IF> sens2_up > 0
IDENTITY> max_gap
EQ> max_gap = 0.38
IF> sens2_low > 0

@@

tilpas_pr_bs2 = Shock_bs2$simulation$tilpas_pr
u_ds_bs2 = Shock_bs2$simulation$u_ds
part_bs2 = Shock_bs2$simulation$part
nben_h_bs2 = Shock_bs2$simulation$nben_h
wage_ds_bs2 = Shock_bs2$simulation$wage_ds
dp_person_bs2 = Shock_bs2$simulation$dp_person
kont_h_ratio_bs2 = Shock_bs2$simulation$kont_h_ratio

nl_g_bs2 = Shock_bs2$simulation$nl_g
inflation_bs2 = Shock_bs2$simulation$inflation

@@

@@

wage_gap_02 = Shock_2$simulation$wage_gap
max_gap_02 = Shock_2$simulation$max_gap

inflation_02 = Shock_2$simulation$inflation
prod_02 = Shock_2$simulation$prod

@@

```{r}
plot((emp_02-emp_bs2)*1000, col= "red")
```

@@

>>>>

COMMENT> 
IDENTITY> max_gap
EQ> max_gap = 0.42
IF> sens2_low <= 0 & sens2_up <= 0
IDENTITY> max_gap
EQ> max_gap = 0.42
IF> sens2_up > 0
IDENTITY> max_gap
EQ> max_gap = 0.38
IF> sens2_low > 0

@@

tilpas_pr_bs2 = Shock_bs2$simulation$tilpas_pr
u_ds_bs2 = Shock_bs2$simulation$u_ds
part_bs2 = Shock_bs2$simulation$part
nben_h_bs2 = Shock_bs2$simulation$nben_h
wage_ds_bs2 = Shock_bs2$simulation$wage_ds
dp_person_bs2 = Shock_bs2$simulation$dp_person
kont_h_ratio_bs2 = Shock_bs2$simulation$kont_h_ratio
unemp_bs2 = Shock_bs2$simulation$unemp
nl_g_bs2 = Shock_bs2$simulation$nl_g
inflation_bs2 = Shock_bs2$simulation$inflation

@@

```{r}
shock_max_dp_model_shock=shock_max_dp_model %>% window(start= c(2006,3))
```

@@

wage_gap_02 = Shock_2$simulation$wage_gap
max_gap_02 = Shock_2$simulation$max_gap
unemp_02 = Shock_2$simulation$unemp
inflation_02 = Shock_2$simulation$inflation
prod_02 = Shock_2$simulation$prod

@@

```{r}
plot((emp_02-emp_bs2)*1000, col= "red")
plot((unemp_02-unemp_bs2)*1000, col= "red")

@@

### Elasticities

```{r}
pr_change_unemp_02=(unemp_02-unemp_bs2)/unemp_bs2
pr_change_komp_r_02=(komp_r_02-komp_r_bs2)/komp_r_bs2
pr_change_wage_ds_02=(wage_ds_02-wage_ds_bs2)/wage_ds_bs2

pr_change_wage_ds_02/pr_change_komp_r_02

pr_change_unemp_02/pr_change_komp_r_02
```

Så ser ud til det ikke alt sammen kommer gennem løn kanalen?
